My Findings

### 2024-07-06 Findings (Shared Folder)/Chapters/theoriticalInvestiagtion.tex
new notes

	Every intervention induces a vector field on the manifold $ \mathcal{N} $ denoted by $ \mathcal{I} $. So the time evolution of a given vascular system due to particular intervention (like radiotherapy or chemotherapy) will be given be a one-parameter group of diffeomorphisms of $ \mathcal{N} $. In other words, the time evolution of a given vascular system $ p \in \mathcal{N} $ will be the integral curve of $ \mathcal{I} $ starting at $ p $.
\end{observation}
\begin{remark}
	According to the remark above, we can model the angiogenesis process as a background vector field on the space of all vascular systems. Any other background biological mechanisms can also be lumped in this vector field. We denote this vector field as $ \mathcal{G} $.
\end{remark}
\begin{remark}
	The vector space $ \mathcal{I} $ due to intervention can be possibly learned by an appropriate machine learning system.
\end{remark}

\begin{openQuestion}[Can a Machine Learning System Learn These Vector Fields?]
	Our ultimate goal in this project is to determine the mapping $ F $ as well as the intervention vector field $ \mathcal{I}_i $, along with any background vector field $ \mathcal{G} $. Denote the intervention and the background vector fields as 
	\[ \mathcal{I} = \mathcal{I}_i + \mathcal{G}. \]
	One possible parallel approach to determine these vector fields is to use appropriate machine learning system along with a suitable simulator the learn these vector fields.
\end{openQuestion}

@@

I think at some step, I would need to consider percolation models and their statistical signatures to see if I can use somewhat modified versions of that.

>>>>

	Every intervention induces a vector field on the manifold $ \mathcal{N} $ denoted by $ \mathcal{I} $. So the time evolution of a given vascular system due to particular intervention (like radiotherapy or chemotherapy) will be given be a one-parameter group of diffeomorphisms of $ \mathcal{N} $. In other words, the time evolution of a given vascular system $ p \in \mathcal{N} $ will be the integral curve of $ \mathcal{I} $ starting at $ p $.
\end{observation}
\begin{remark}
	According to the remark above, we can model the angiogenesis process as a background vector field on the space of all vascular systems. Any other background biological mechanisms can also be lumped in this vector field. We denote this vector field as $ \mathcal{G} $.
\end{remark}

\begin{openQuestion}[How to Determine These Vector Fields?]
	Our ultimate goal in this project is to determine the mapping $ F $ as well as the intervention vector field $ \mathcal{I}_i $, along with any background vector field $ \mathcal{G} $. Denote the intervention and the background vector fields as 
	\[ \mathcal{I} = \mathcal{I}_i + \mathcal{G}. \]
	I am still thinking actively how my modeling attempts (like agent based model, or the PDE model) manifest themselves in this general framework? How these models can ultimately help to determine these vector fields, at least locally.
\end{openQuestion}

\begin{openQuestion}[Can a Machine Learning System Learn These Vector Fields?]
	One possible parallel approach to determine these vector fields is to use appropriate machine learning system along with a suitable simulator the learn these vector fields.
\end{openQuestion}

@@

\begin{observation}[Homogenization and Darcy's Law]
	I think at some step, I would need to consider percolation models and their statistical signatures to see if I can use somewhat modified versions of that. After making this connection. I can apply the idea of homogenization and possibly Darcy's law suggested by Leah.
\end{observation}
